---
title       : My Calculator App
subtitle    : R shiny app
author      : Naveen Silvester
job         : Data Scientist
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
url:
  lib: ../../libraries
  assets: ../../assets
widgets     : [mathjax]            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
---
---

## Slide 2: Introduction to My Calculator
<a href="https://naveensilvester.shinyapps.io/MyCalculator/">My Calculator</a> is an application developed in R shiny. This application enables 
user to enter two numbers and apply mathematical operations on it. Three mathematical
operations are provided as choice. The default is Addition. The results from the mathematical
operations is printed on to the main panel. The main panel also provides the option to see
the Documentation/User Guide on checking the checkbox provided in the left side panel.
Click here to access <a href="https://naveensilvester.shinyapps.io/MyCalculator/"> My Calculator Application </a>
Following are the Input fields that the App uses

1.  First Number
2.  Second Number
3.  Mathematical Operator (Default Addition)
4.  Citation (Default is Yes)
5.  Documentation/UserGuid (Default is No)

---


## Slide 3: Mathematical Function - Addition
```{r, echo=TRUE}
  First_Number <- 10
  Second_Number <- 20
  sum(First_Number + Second_Number)
```

---

## Slide 4: Mathematical Function - Subtraction
```{r, echo=TRUE}
  First_Number <- 100
  Second_Number <- 20
  Subtraction <- (First_Number - Second_Number)
  Subtraction
```

---


## Slide 5: Mathematical Function - Multiplication
```{r, echo=TRUE}
  First_Number <- 10
  Second_Number <- 20
  Product <- (First_Number * Second_Number)
  Product
```